\documentclass[11pt,letterpaper,sans]{moderncv}

% moderncv themes
\moderncvstyle{classic} % casual, classic, banking, oldstyle and fancy
\moderncvcolor{purple} 
\nopagenumbers{}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}

\graphicspath{ {./pictures/} }

% personal data
\name{Javier}{Portillo}
\title{Software Developer}
\email{javiermarquezportillo@gmail.com}
\phone[mobile]{+503~7689~9554}
% \photo[64pt][0.4pt]{mi_foto}

%\setlength{\footskip}{66pt}


\begin{document}

\makecvtitle

\section{Profile}
Experienced software developer specializing in JavaScript and TypeScript, with a proven track record of successfully deploying production-ready products that streamline operations and enhance efficiency.
My robust foundation from being a self-taught programmer from a very young age, and then also formally educated, insatiable curiosity in the continuous urge to deepen my knowledge, and meticulous approach enable me to thrive in dynamic environments.
Seeking opportunities to leverage my skills and drive success in software development initiatives.

\section{Job Experience}
\cventry{2017--2023}{Software Engineer}{Dada Dada \& Cia.}{San Salvador}{}{}
\begin{itemize}
  \item Developed call-center oriented services from the ground up with modern technologies and best practices.
  \item Implemented integrations with 3rd party software but also with our client's custom systems.
  \item Collaborated in the maintenance of legacy systems.
  \item Coordinated the efforts of adoption of programming best practices in my team, like clean code, refactoring and unit testing. With approval and collaboration with management, I helped establish a series of free-form workshops where the team could share specialized knowledge, thereby enhancing the team's capabilities and made us a more cohesive team.
  \item Developed the ``Omnichannel Project'', a multichannel social-media bridge meant to distribute direct messages sent via instant messaging to be attended by groups of agents.
  \item Developed the ``Automatic Dialler'', a platform for setup, management and distribution of massive call campaigns.
  \item Created multiple custom Chat Bots using Rasa, this was successfully integrated with the Omnichannel Project to make a hybrid system of automated answering of messages and a seamless take-over from agents.
  \item Managed cloud and on-premise deployments of our systems.
  \item Managed database systems, including creating and maintaining schemas.
  \item Deployed services with different levels of orchestration depending on our client's needs.
\end{itemize}

\cventry{2023--2023}{Backend Developer}{Jobchain GmbH}{Vienna}{}{}
\begin{itemize}
  \item Developed back-end services focused on end-user messaging and contact management.
\end{itemize}

\cventry{2023--2024}{Backend Developer}{Universidad Francisco Gavidia}{San Salvador}{}{}
\begin{itemize}
  \item Upgraded legacy C\# modules into NodeJS services for the back-end financial system.
\end{itemize}

\newpage

\section{Technical Skills}
\cvitem{Programming Languages}{JavaScript, TypeScript, PHP, Lua, Python}
\vspace{.5em}
\cvitem{Markup}{HTML, CSS, Markdown, \LaTeX{}}
\vspace{.5em}
\cvitem{Frameworks \& Libraries}{React, NestJS, NextJS, VueJS, Nuxt, ExpressJS, Socket.io, Tailwind, Webpack, Vite, REST, Jest, Playwright, Cucumber}
\vspace{.5em}
\cvitem{Other Technologies}{Docker, Kubernetes, MySQL, MongoDB, RabbitMQ, Ejabberd (XMPP), Facebook Graph API, Electron, Asterisk, Rasa, Linux server administration}
\vspace{.5em}
\cvitem{Workflow}{NeoVim (main), VSCode, Tmux, common Linux utils, git, SSH, VPN, can adapt depending on the need}

\section{Soft Skills}
\cvitem{}{Good listener, problem solver, can work under pressure, strong mentality under crisis, able to communicate technical concepts}

\section{Spoken Languages}
\cvitem {}{English, Spanish (native)}

\section{Education \& Certification}
\cventry{2022}{Bachelor's Degree in Computer Science}{Universidad Luterana Salvadoreña}{San Salvador}{}{}
\cventry{2022}{Certified Kubernetes Administrator}{The Cloud Native Computing Foundation}{}{}{}
\cventry{2021}{Certified Kubernetes Administrator (CKA) with Practice Test}{Udemy}{}{}{}
\cventry{2021}{Go: The Complete Developer's Guide (Golang)}{Udemy}{}{}{}
\cventry{2021}{Kubernetes, from beginner to expert}{Udemy}{}{}{}

\end{document}
