\documentclass[letterpaper]{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1.2in]{geometry}
\usepackage{enumitem}

\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}
{\huge}
{}
{.25em}
{\filcenter\bfseries\lowercase}

\titleformat{\subsection}
{\bfseries\Large}
{\hspace{-.2in}$\bullet$}
{.25em}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}[ ---]

\titlespacing{\subsubsection}
{0em} {.25em} {.5em}

\renewcommand{\maketitle}{
	\begin{center}
		{\huge\bfseries\theauthor}

		\vspace{.5em}

		javiermarquezportillo@gmail.com
	\end{center}
}

\begin{document}

\title{R\'esum\'e}
\author{Javier Portillo}

\maketitle

\section{Profile}

Experienced software developer specializing in JavaScript and TypeScript, dedicated to delivering high-quality solutions. My robust foundation, insatiable curiosity, and meticulous approach enable me to thrive in dynamic environments. Eager to contribute expertise to drive success in your organization's software development endeavors.

\section{Job Experience}

\subsubsection{Dada Dada \& Cia. S.A. de C.V.}

Software Engineer; Sep '17 - Feb '23

\begin{itemize}
  \item Ground-up development of services, integrations, maintenance of legacy systems, unit testing.
  \item Development of ``Omnichannel Project'', a multichannel social-media bridge meant to distribute direct messages sent via instant messaging to be attended by groups of agents.
  \item Development of ``Automatic Dialler'', a platform for setup, management and distribution of massive call campaigns.
  \item Development of Chat Bots using Rasa.
  \item Cloud and On-Premise server administration.
  \item Database management, creation and maintenance of schemas.
  \item Deployment of services with different levels of orchestration depending on client's needs.
\end{itemize}

\subsubsection{Jobchain GmbH}

Backend Developer; Feb '23 - Oct '23

\begin{itemize}
  \item Development of back-end services focused on end-user messaging and contact management.
\end{itemize}

\subsubsection{Universidad Francisco Gavidia}

Backend Developer; Oct '23 - Current

\begin{itemize}
  \item Responsible for upgrading old C\# modules into NodeJS services for the back-end financial system.
\end{itemize}

\section{Technical Skills}

\subsection{Software Development}

\subsubsection{Programming Languages}

JavaScript, TypeScript, PHP, Python (beginner), Lua, Bash

\subsubsection{Markup}

HTML, CSS, Markdown, \LaTeX{}.

\subsubsection{Frameworks \& Libraries}

React, NestJS, NextJS, VueJS, ExpressJS, Socket.io, Tailwind, Webpack, Vite, ReST, Jest, Playwright, Cucumber.

\subsection{Workflow}

NeoVim (main), VSCode, Tmux, common Linux utils, git, SSH, VPN, can adapt depending on the need.

\subsection{Other Technologies}

Docker, Kubernetes, MySQL, PostgreSQL, MongoDB, RabbitMQ, Ejabberd (XMPP), Facebook Graph API, Electron, Asterisk, Rasa.

\subsection{Spoken Languages}

English, Spanish (native)

\section{Education \& Certification}

\begin{itemize}
	\item \textbf{Computer Science Degree} \newline Universidad Luterana Salvadoreña, 2022.

	\item \textbf{Certified Kubernetes Administrator} \newline The Cloud Native Computing Foundation, 2022.
\end{itemize}

\end{document}
